Automating Verification of MPC Security

### 2023-06-08 popl24/pmf.tex
checkpoint

\paragraph{Example \ref{example-he} revisited} This standard example
of an MPC secure protocol illustrates how a functionality- in this
case addition (in the binary field)- can be implemented securely. As
mentioned previously, it is \emph{not} the case that \emph{no}
information about input secrets can be revealed to the adversary in
the MPC threat model, since the result of the functionality can itself
reveal information. For example, if the result of addition is $0$,
the adversary knows that all clients must have the same value.
More precisely:
\begin{mathpar}
  (\sum_{\beta}(\progd(\prog_{\ref{example-he}}))(\{\sx{1}{1} \mapsto \beta, \sx{2}{1} \mapsto \beta, \sx{3}{1} \mapsto \beta \}|\{ \vx{0}{output} \mapsto 0 \})) = 1
\end{mathpar}

>>>>

\paragraph{Example \ref{example-he} revisited} This standard example
of an MPC secure protocol illustrates how a functionality- in this
case addition (in the binary field)- can be implemented securely. As
mentioned previously, it is \emph{not} the case that \emph{no}
information about input secrets can be revealed to the adversary in
the MPC threat model, since the result of the functionality can itself
reveal information. For example, if the result of addition is $0$,
the adversary knows that all clients must have the same value.
More precisely:
\begin{mathpar}
  (\sum_{\beta}(\progd(\prog_{\ref{example-he}}))(\{\sx{1}{1} \mapsto \beta, \sx{2}{1} \mapsto \beta, \sx{3}{1} \mapsto \beta \}|\{ \vx{0}{output} \mapsto 0 \})) = 1
\end{mathpar}
If we assume that a client is corrupted we can formally consider the
impacts on information released to the adversary by conditioning the
program distribution on corrupt secrets.  For example, if we assume
client 2 with input secret 1 is corrupted and the output is 0, then
adversary knows with certainty that clients 1 and 3 also have input
secrets 1. We can express this as:
